---
title: "Heat Wave Monitor"
date-modified: now
author: 
  - name: John Palmer
    orcid: 0000-0002-2648-7860
    affiliations:
      - name: Universitat Pompeu Fabra
format:
  html:
    toc: true
    toc-depth: 5
execute: 
  echo: false
  cache: false
---

```{r}
#| label: load
#| message: false

library(tidyverse)
library(kableExtra)
library(data.table)
library(lubridate)
library(plotly)

heat_wave_summary = fread("data/heat_wave_summary.csv.gz")

Hi_min_thresholds_table = fread("data/Hi_min_thresholds_table.csv.gz")

summary_readings_past_week = fread("data/summary_readings_past_week.csv.gz")

```

## Summary

CAUTION: There is a gap in the dates because the historical data has not yet caught up with our first recording of the realtime data.

Note: This report was last modified at `r with_tz(now(), "CET")`.

### Data Checking

Number of station-readings available for each municipality during past week:

```{r}

summary_readings_past_week %>% kableExtra::kbl() 

```

### Heat Wave Tables

#### 85th Percentile Threshold

Summary of heat waves this year, based on two and five consecutive days at 85th percentile of daily minimum heat index:

##### 2-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 85, days == 2, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```

##### 3-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 85, days == 3, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```


##### 4-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 85, days == 4, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```


##### 5-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 85, days == 5, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```

#### 90th Percentile Threshold

Summary of heat waves this year, based on two and five consecutive days at 90th percentile of daily minimum heat index:

##### 2-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 90, days == 2, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```


##### 3-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 90, days == 3, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```


##### 4-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 90, days == 4, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```

##### 5-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 90, days == 5, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```

#### 95th Percentile Threshold

Summary of heat waves this year, based on two and five consecutive days at 95th percentile of daily minimum heat index:


##### 2-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 95, days == 2, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```


##### 3-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 95, days == 3, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```



##### 4-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 95, days == 4, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```


##### 5-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 95, days == 5, year(date)==year(today())) 

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}


```
#### 99th Percentile Threshold

Summary of heat waves this year, based on two and five consecutive days at 99th percentile of daily minimum heat index:


##### 2-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 99, days == 2, year(date)==year(today()))

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}

```



##### 3-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 99, days == 3, year(date)==year(today()))

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}

```



##### 4-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 99, days == 4, year(date)==year(today()))

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}

```


##### 5-day periods

```{r}

this_heat_wave_summary = heat_wave_summary %>% filter(threshold == 99, days == 5, year(date)==year(today()))

if(nrow(this_heat_wave_summary)>0){
this_heat_wave_summary %>% kableExtra::kbl() 
} else{
  cat("No heat waves yet at this threshold.")
}

```

### Thresholds

Heat wave thresholds:

```{r}

Hi_min_thresholds_table %>% kableExtra::kbl() 

```

## Barcelona

### Threshold for at least 2 days

```{r}

read_rds("plots/full_timeseries_Barcelona.Rds") %>% ggplotly()

```


```{r}

read_rds("plots/recent_timeseries_Barcelona.Rds") %>% ggplotly()

```


### Threshold for at least 3 days



```{r}

read_rds("plots/full_timeseries_3d_Barcelona.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_3d_Barcelona.Rds") %>% ggplotly()

```



### Threshold for at least 4 days

```{r}

read_rds("plots/full_timeseries_4d_Barcelona.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_4d_Barcelona.Rds") %>% ggplotly()

```



### Threshold for at least 5 days

```{r}

read_rds("plots/full_timeseries_5d_Barcelona.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_5d_Barcelona.Rds") %>% ggplotly()

```


## Madrid


### Threshold for at least 2 days


```{r}

read_rds("plots/full_timeseries_Madrid.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_Madrid.Rds") %>% ggplotly()

```




### Threshold for at least 3 days


```{r}

read_rds("plots/full_timeseries_3d_Madrid.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_3d_Madrid.Rds") %>% ggplotly()

```


### Threshold for at least 4 days

```{r}

read_rds("plots/full_timeseries_4d_Madrid.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_4d_Madrid.Rds") %>% ggplotly()

```


### Threshold for at least 5 days

```{r}

read_rds("plots/full_timeseries_5d_Madrid.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_5d_Madrid.Rds") %>% ggplotly()

```



## Valencia

### Threshold for at least 2 days

```{r}

read_rds("plots/full_timeseries_València.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_València.Rds") %>% ggplotly()

```




### Threshold for at least 3 days

```{r}

read_rds("plots/full_timeseries_3d_València.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_3d_València.Rds") %>% ggplotly()

```





### Threshold for at least 4 days

```{r}

read_rds("plots/full_timeseries_4d_València.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_4d_València.Rds") %>% ggplotly()

```



### Threshold for at least 5 days

```{r}

read_rds("plots/full_timeseries_5d_València.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_5d_València.Rds") %>% ggplotly()

```



## Sevilla


### Threshold for at least 2 days

```{r}

read_rds("plots/full_timeseries_Sevilla.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_Sevilla.Rds") %>% ggplotly()

```



### Threshold for at least 3 days


```{r}

read_rds("plots/full_timeseries_3d_Sevilla.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_3d_Sevilla.Rds") %>% ggplotly()

```




### Threshold for at least 4 days

```{r}

read_rds("plots/full_timeseries_4d_Sevilla.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_4d_Sevilla.Rds") %>% ggplotly()

```





### Threshold for at least 5 days


```{r}

read_rds("plots/full_timeseries_5d_Sevilla.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_5d_Sevilla.Rds") %>% ggplotly()

```


## Zaragoza

### Threshold for at least 2 days

```{r}

read_rds("plots/full_timeseries_Zaragoza.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_Zaragoza.Rds") %>% ggplotly()

```



### Threshold for at least 3 days

```{r}

read_rds("plots/full_timeseries_3d_Zaragoza.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_3d_Zaragoza.Rds") %>% ggplotly()

```






### Threshold for at least 4 days

```{r}

read_rds("plots/full_timeseries_4d_Zaragoza.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_4d_Zaragoza.Rds") %>% ggplotly()

```



### Threshold for at least 5 days

```{r}

read_rds("plots/full_timeseries_5d_Zaragoza.Rds") %>% ggplotly()

```

```{r}

read_rds("plots/recent_timeseries_5d_Zaragoza.Rds") %>% ggplotly()

```


